### 2015-01-26 p3/submission.Rmd
add label fixes

```{r echo=FALSE}
get_simple_boxplot <- function(column) {
  return(qplot(data = df, x = 'simple',
               y = column, geom = 'boxplot',
               xlab = ''))
}

grid.arrange(get_simple_boxplot(df$fixed.acidity),
             get_simple_boxplot(df$volatile.acidity),
             get_simple_boxplot(df$citric.acid),
             get_simple_boxplot(df$TAC.acidity),
             get_simple_boxplot(df$residual.sugar),
             get_simple_boxplot(df$chlorides),
             get_simple_boxplot(df$free.sulfur.dioxide),
             get_simple_boxplot(df$total.sulfur.dioxide),
             get_simple_boxplot(df$density),
             get_simple_boxplot(df$pH),
             get_simple_boxplot(df$sulphates),
             get_simple_boxplot(df$alcohol),
             ncol = 4)
```

@@

```{r echo=FALSE, Bivariate_Plots}
get_bivariate_boxplot <- function(x, y, xlab, ylab) {
  return(qplot(data = df, x = x, y = y, geom = 'boxplot'))
}

grid.arrange(get_bivariate_boxplot(df$quality, df$fixed.acidity),
             get_bivariate_boxplot(df$quality, df$volatile.acidity),
             get_bivariate_boxplot(df$quality, df$citric.acid),
             get_bivariate_boxplot(df$quality, df$TAC.acidity),
             get_bivariate_boxplot(df$quality, log10(df$residual.sugar)),
             get_bivariate_boxplot(df$quality, log10(df$chlorides)),
             get_bivariate_boxplot(df$quality, df$free.sulfur.dioxide),
             get_bivariate_boxplot(df$quality, df$total.sulfur.dioxide),
             get_bivariate_boxplot(df$quality, df$density),
             get_bivariate_boxplot(df$quality, df$pH),
             get_bivariate_boxplot(df$quality, log10(df$sulphates)),
             get_bivariate_boxplot(df$quality, df$alcohol),
             ncol = 4)

grid.arrange(get_bivariate_boxplot(df$rating, df$fixed.acidity),
             get_bivariate_boxplot(df$rating, df$volatile.acidity),
             get_bivariate_boxplot(df$rating, df$citric.acid),
             get_bivariate_boxplot(df$rating, df$TAC.acidity),
             get_bivariate_boxplot(df$rating, log10(df$residual.sugar)),
             get_bivariate_boxplot(df$rating, log10(df$chlorides)),
             get_bivariate_boxplot(df$rating, df$free.sulfur.dioxide),
             get_bivariate_boxplot(df$rating, df$total.sulfur.dioxide),
             get_bivariate_boxplot(df$rating, df$density),
             get_bivariate_boxplot(df$rating, df$pH),
             get_bivariate_boxplot(df$rating, log10(df$sulphates)),
             get_bivariate_boxplot(df$rating, df$alcohol),
             ncol = 4)
```

@@

```{r echo=FALSE}
simple_cor_test <- function(x, y) {
  return(cor.test(x, y)$estimate)
}

correlations <- c(
  simple_cor_test(df$fixed.acidity, as.numeric(df$quality)),
  simple_cor_test(df$volatile.acidity, as.numeric(df$quality)),
  simple_cor_test(df$citric.acid, as.numeric(df$quality)),
  simple_cor_test(df$TAC.acidity, as.numeric(df$quality)),
  simple_cor_test(log10(df$residual.sugar), as.numeric(df$quality)),
  simple_cor_test(log10(df$chlorides), as.numeric(df$quality)),
  simple_cor_test(df$free.sulfur.dioxide, as.numeric(df$quality)),
  simple_cor_test(df$total.sulfur.dioxide, as.numeric(df$quality)),
  simple_cor_test(df$density, as.numeric(df$quality)),
  simple_cor_test(df$pH, as.numeric(df$quality)),
  simple_cor_test(log10(df$sulphates), as.numeric(df$quality)),
  simple_cor_test(df$alcohol, as.numeric(df$quality)))
names(correlations) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'TAC.acidity', 'log10.residual.sugar',
                         'log10.chlordies', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'log10.sulphates', 'alcohol')
correlations
```

>>>>

```{r echo=FALSE}
get_simple_boxplot <- function(column, ylab) {
  return(qplot(data = df, x = 'simple',
               y = column, geom = 'boxplot',
               xlab = '',
               ylab = ylab))
}

grid.arrange(get_simple_boxplot(df$fixed.acidity, 'fixed acidity'),
             get_simple_boxplot(df$volatile.acidity, 'volatile acidity'),
             get_simple_boxplot(df$citric.acid, 'citric acid'),
             get_simple_boxplot(df$TAC.acidity, 'TAC acidity'),
             get_simple_boxplot(df$residual.sugar, 'residual sugar'),
             get_simple_boxplot(df$chlorides, 'chlorides'),
             get_simple_boxplot(df$free.sulfur.dioxide, 'free sulf. dioxide'),
             get_simple_boxplot(df$total.sulfur.dioxide, 'total sulf. dioxide'),
             get_simple_boxplot(df$density, 'density'),
             get_simple_boxplot(df$pH, 'pH'),
             get_simple_boxplot(df$sulphates, 'sulphates'),
             get_simple_boxplot(df$alcohol, 'alcohol'),
             ncol = 4)
```

@@

```{r echo=FALSE, Bivariate_Plots}
get_bivariate_boxplot <- function(x, y, ylab) {
  return(qplot(data = df, x = x, y = y, geom = 'boxplot', ylab = ylab))
}

grid.arrange(get_bivariate_boxplot(df$quality, df$fixed.acidity,
                                   'fixed acidity'),
             get_bivariate_boxplot(df$quality, df$volatile.acidity,
                                   'volatile acidity'),
             get_bivariate_boxplot(df$quality, df$citric.acid,
                                   'citric acid'),
             get_bivariate_boxplot(df$quality, df$TAC.acidity,
                                   'TAC acidity'),
             get_bivariate_boxplot(df$quality, log10(df$residual.sugar),
                                   'residual sugar'),
             get_bivariate_boxplot(df$quality, log10(df$chlorides),
                                   'chlorides'),
             get_bivariate_boxplot(df$quality, df$free.sulfur.dioxide,
                                   'free sulf. dioxide'),
             get_bivariate_boxplot(df$quality, df$total.sulfur.dioxide,
                                   'total sulf. dioxide'),
             get_bivariate_boxplot(df$quality, df$density,
                                   'density'),
             get_bivariate_boxplot(df$quality, df$pH,
                                   'pH'),
             get_bivariate_boxplot(df$quality, log10(df$sulphates),
                                   'sulphates'),
             get_bivariate_boxplot(df$quality, df$alcohol,
                                   'alcohol'),
             ncol = 4)

grid.arrange(get_bivariate_boxplot(df$rating, df$fixed.acidity,
                                   'fixed acidity'),
             get_bivariate_boxplot(df$rating, df$volatile.acidity,
                                   'volatile acidity'),
             get_bivariate_boxplot(df$rating, df$citric.acid,
                                   'citric acid'),
             get_bivariate_boxplot(df$rating, df$TAC.acidity,
                                   'TAC acidity'),
             get_bivariate_boxplot(df$rating, log10(df$residual.sugar),
                                   'residual sugar'),
             get_bivariate_boxplot(df$rating, log10(df$chlorides),
                                   'chlorides'),
             get_bivariate_boxplot(df$rating, df$free.sulfur.dioxide,
                                   'free sulf. dioxide'),
             get_bivariate_boxplot(df$rating, df$total.sulfur.dioxide,
                                   'total sulf. dioxide'),
             get_bivariate_boxplot(df$rating, df$density,
                                   'density'),
             get_bivariate_boxplot(df$rating, df$pH,
                                   'pH'),
             get_bivariate_boxplot(df$rating, log10(df$sulphates),
                                   'sulphates'),
             get_bivariate_boxplot(df$rating, df$alcohol,
                                   'alcohol'),
             ncol = 4)
```

@@

```{r echo=FALSE}
simple_cor_test <- function(x, y) {
  return(cor.test(x, as.numeric(y))$estimate)
}

correlations <- c(
  simple_cor_test(df$fixed.acidity, df$quality),
  simple_cor_test(df$volatile.acidity, df$quality),
  simple_cor_test(df$citric.acid, df$quality),
  simple_cor_test(df$TAC.acidity, df$quality),
  simple_cor_test(log10(df$residual.sugar), df$quality),
  simple_cor_test(log10(df$chlorides), df$quality),
  simple_cor_test(df$free.sulfur.dioxide, df$quality),
  simple_cor_test(df$total.sulfur.dioxide, df$quality),
  simple_cor_test(df$density, df$quality),
  simple_cor_test(df$pH, df$quality),
  simple_cor_test(log10(df$sulphates), df$quality),
  simple_cor_test(df$alcohol, df$quality))
names(correlations) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'TAC.acidity', 'log10.residual.sugar',
                         'log10.chlordies', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'log10.sulphates', 'alcohol')
correlations
```
